CSCI 447: Project 1

### 2019-09-13 paper/paper.tex
'variance' now included :]

\subsection{Breast Cancer Wisconsin} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Glass} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Iris} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Soybean} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Voting Records} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

>>>>

\subsection{Breast Cancer Wisconsin} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified Breast Cancer Wisconsin data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the Breast Cancer Wisconsin data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Glass} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified Glass data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the Glass data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Iris} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified Iris data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the Iris data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Soybean} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified Soybean data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the Soybean data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Voting Records} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified Voting Records data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the Voting Records data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$
